\documentclass[international_finance_p2.tex]{subfiles}

\begin{document}
\setbeamercovered{transparent}
\section{International Portfolio Investment}

\subsection{Portfolio Diversification}
\begin{frame}{Portfolio Diversification}
\begin{itemize}[<+->]
\item
Diversification means reducing non-systematic risk by investing in a variety of assets.
\item
The variance that can be eliminated through diversification is called nonsystematic risk; this is the risk that is unique to a particular firm or industry. Systematic risk is common to all firms and remains even in diversified portfolios.
\item
International diversification:
\begin{enumerate}
\item
More wide than domestic.
\item
By investing across countries, we eliminate part of the cyclical fluctuation in our portfolio that would arise from the domestic business cycle.
\end{enumerate}
\end{itemize}
\end{frame}

\subsection{Depositary receipts}
\begin{frame}{Depositary receipts}
\begin{itemize}[<+->]
\item
A depositary receipt is a negotiable financial instrument issued by a bank to represent a foreign company's publicly traded securities.
\item
When the depositary bank is in the U.S., the instruments are known as American Depositary Receipts (ADRs). European banks issue European depository receipts (EDRs), and other banks issue global depository receipts (GDRs).
\end{itemize}
\end{frame}

\subsection{The Globalization of Equity Markets}
\begin{frame}{The Globalization of Equity Markets}
\begin{itemize}[<+->]
\item
A segmented market is one in which foreign investors are not allowed to buy domestic stocks and domestic investors are not allowed to buy foreign stocks. 
\item
Part of the process of the globalization of world economies is the liberalization of stock market restrictions to open markets to the world.
\end{itemize}
\end{frame}
\begin{frame}[allowframebreaks]{Emerging economies have the following signs}
\begin{itemize}
\item
Attempting to order its national accounts, privatize state companies, and deregulate economic activity.
\item
Stabilizing its political system, moving from more autocratic regimes to liberal, democratic rules; 
\item
increasing public interest in solving the most pressing social problems.
\item
Rapidly dismantling the barriers to foreign trade and investment, thereby quickly increasing its share in the world economy. 
\item
Being flooded by foreign capital, hard technologies, and new, advanced managerial practices, as multinational corporations (MNCs) enter its territory.
\item
Experiencing a profound change in the structure of entire industries and individual companies, pushing firms to approach international standards of competitiveness.
\item
Growing rate of activity in mergers and acquisitions (M8cAs), joint ventures, and the establishment of wholly owned subsidiaries to extract value from the productivity gaps existing between the emerging economy and other more developed markets.
\item
Boasting domestic stock market, which beckons international financial investors. 
\item
Expanding influence to other neighboring economies, which, in turn, start to open to the world.
\end{itemize}
\end{frame}

\end{document}