% !TeX program = lualatex -synctex=1 -interaction=nonstopmode --shell-escape %.tex

\documentclass[12pt, table]{exam}
\usepackage[rus]{borochkin}

\usepackage{borochkin_exam_eng}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\professor
\iftagged{professor}{ \printanswers }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\examrunningheader{International Finance, exam \#2}
\examrunningfooter{A. Borochkin}

\begin{document}
\setcounter{section}{0\relax}%
\noindent
% Control № #1, Variant #2, Subject #3
\studentpersonalinfo{2}{2}{IF}
\normalsize

\begin{questions}
\question[40] Тест
\answerstotest

	
\question[20] 
\noaddpoints
\begin{subparts}
\subpart[10] 

\begin{solution}[21em]
\end{solution}

\subpart[10] 

\begin{solution}[12em]
\end{solution}

\end{subparts}
\addpoints

\question[10] 
\noaddpoints
\begin{subparts}
	\subpart[8] 
	\begin{solution}[8em]

	\end{solution}

	\subpart[2] 
	\begin{solution}[4em]
	\end{solution}
\end{subparts}
\addpoints

\question[15] 
\begin{subparts}
	\subpart[5] 
	\begin{solution}[8em]
		
	\end{solution}
	
	\subpart[5] 
	\begin{solution}[18em]
	\end{solution}
	\subpart[5] 
	\begin{solution}[18em]
	\end{solution}
	
\end{subparts}
\addpoints

\question[10] 
\begin{solution}[10em]
\end{solution}


\end{questions}

\pagebreak
\noindent\textbf{Тестовые вопросы (выберите один правильный ответ)}

\begin{questions}
\begin{multicols}{2}
\setlength{\columnsep}{1cm}

\question The reason for credit discrimination or credit blockade may be:
	 \begin{choices}
	 \CC insufficient reliability of the borrower;
	 \choice announcement of a borrower default;
	 \choice political divergences of the creditor with the borrower;
	 \choice all listed.
	 \end{choices}
\question The Eurocurrency market is characterized by:
	 \begin{choices}
	 \choice stability of interest rates;
	 \CC active use of developing countries currencies;
	 \choice the high volume of trading;
	 \choice state regulation of interest rates.
	 \end{choices}
\question The main creditors in the world credit market are:
	 \begin{choices}
	 \choice national governments;
	 \CC companies and corporations;
	 \choice banks;
	 \choice individuals.
	 \end{choices}
\question Interest rate for the short term is as a rule:
	 \begin{choices}
	 \CC above, than on the longterm;
	 \choice below, than on the longterm;
	 \choice same, as well as on the longterm;
	 \choice differs from a rate on the longterm in an unpredictable way.
	 \end{choices}
\question In the international practice the short term is:
	 \begin{choices}
	 \choice till 1 week;
	 \CC till 1 month;
	 \choice till 1 quarter;
	 \choice till 1 year.
	 \end{choices}
\question An interest rate on international credits to the governments, as a rule, is:
	 \begin{choices}
	 \choice more, than on the credit to private sector;
	 \CC less, than on the credit to private sector;
	 \choice same, as on the credit to private sector;
	 \choice differs in an unpredictable way from a rate on the credit to private sector.
	 \end{choices}
\question If the profitability of the project increases, than the term of its payback will:
	 \begin{choices}
	 \CC grow;
	 \choice decrease;
	 \choice remain invariable;
	 \choice change in an unpredictable way.
	 \end{choices}
\question The increase in a credit rating of the country conducts:
	 \begin{choices}
	 \choice to growth of interest rates for the loans granted to residents of this country;
	 \choice to decrease in interest rates for the loans granted to residents of this country;
	 \CC to no change of interest rates for the loans granted to residents of this country;
	 \choice to unpredictable changes of interest rates for the loans provided to residents of this country.
	 \end{choices}
\question The increase in rates of inflation in the country promotes:
	 \begin{choices}
	 \choice growth of nominal interest rates in national currency;
	 \choice decrease in nominal interest rates in national currency;
	 \CC preservation of nominal interest rates in national currency;
	 \choice unpredictable fluctuations of nominal interest rates in national currency.
	 \end{choices}
\question If the exchange rate in which the loan is granted, grows, expenses of the borrower:
	 \begin{choices}
	 \CC grow;
	 \choice decrease;
	 \choice don't change;
	 \choice change in an unpredictable way.
	 \end{choices}



\end{multicols}
\end{questions}

\end{document}
