% !TeX program = lualatex -synctex=1 -interaction=nonstopmode --shell-escape %.tex

\documentclass[12pt, table]{exam}
\usepackage[rus]{borochkin}

\usepackage{borochkin_exam_eng}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\professor
\iftagged{professor}{ \printanswers }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\examrunningheader{International Finance, exam \#2}
\examrunningfooter{A. Borochkin}

\begin{document}
\setcounter{section}{0\relax}%
\noindent
% Control № #1, Variant #2, Subject #3
\studentpersonalinfo{2}{1}{IF}
\normalsize

\begin{questions}
\question[40] Тест
\answerstotest

	
\question[20] 
\noaddpoints
\begin{subparts}
\subpart[10] 

\begin{solution}[21em]
\end{solution}

\subpart[10] 

\begin{solution}[12em]
\end{solution}

\end{subparts}
\addpoints

\question[10] 
\noaddpoints
\begin{subparts}
	\subpart[8] 
	\begin{solution}[8em]

	\end{solution}

	\subpart[2] 
	\begin{solution}[4em]
	\end{solution}
\end{subparts}
\addpoints

\question[15] 
\begin{subparts}
	\subpart[5] 
	\begin{solution}[8em]
		
	\end{solution}
	
	\subpart[5] 
	\begin{solution}[18em]
	\end{solution}
	\subpart[5] 
	\begin{solution}[18em]
	\end{solution}
	
\end{subparts}
\addpoints

\question[10] 
\begin{solution}[10em]
\end{solution}


\end{questions}

\pagebreak
\noindent\textbf{Тестовые вопросы (выберите один правильный ответ)}

\begin{questions}
\begin{multicols}{2}
\setlength{\columnsep}{1cm}

\question The main source of the international credit repayment is:
	 \begin{choices}
	 \CC loans refinancing;
	 \choice depreciation;
	 \choice enterprise profit;
	 \choice speculative income.
	 \end{choices}
\question As credit collateral are NOT used:
	 \begin{choices}
	 \choice securities;
	 \CC work in progress;
	 \choice inventory items;
	 \choice accounts payable.
	 \end{choices}
\question The main borrowers in the international market are:
	 \begin{choices}
	 \choice national governments;
	 \CC companies and corporations;
	 \choice banks;
	 \choice individuals.
	 \end{choices}
\question Interest rate for the blank credits:
	 \begin{choices}
	 \CC above, than on credits with collateral;
	 \choice below, than on credits with collateral;
	 \choice same, as well as on credits with collateral;
	 \choice differs from credits with collateral in an unpredictable way.
	 \end{choices}
\question The political tension escalation in the country conducts:
	 \begin{choices}
	 \choice to growth of its credit rating;
	 \CC to decrease of its credit rating;
	 \choice to invariable value of its credit rating;
	 \choice to unpredictable fluctuations of its credit rating.
	 \end{choices}
\question If in the country inflation increase and nominal interest rates remain invariable, a real interest rate in national currency:
	 \begin{choices}
	 \choice will grow;
	 \CC will decrease;
	 \choice remains invariable;
	 \choice will change in an unpredictable way.
	 \end{choices}
\question The increase of the official discount rate promotes:
	 \begin{choices}
	 \CC to increase of nominal interest rates in national currency;
	 \choice to decrease in nominal interest rates in national currency;
	 \choice no change of nominal interest rates in national currency;
	 \choice to unpredictable fluctuations of nominal interest rates in national currency.
	 \end{choices}
\question The main borrowers of the International Monetary Fund as of the beginning of the XXI century are:
	 \begin{choices}
	 \choice developed countries;
	 \choice developing countries and the countries with transitional economy — exporters of oil;
	 \CC developing countries and the countries with a transitional economy — importers of oil;
	 \choice the countries with a planned economy.
	 \end{choices}
\question Indispensable condition of credit isn't:
	 \begin{choices}
	 \choice credit repayment;
	 \choice collateral;
	 \CC credit history of the borrower;
	 \choice interest payment by the borrower to the creditor.
	 \end{choices}
\question The bank credits are given in:
	 \begin{choices}
	 \CC monetary form;
	 \choice commodity form;
	 \choice a payment delay;
	 \choice patents and licenses.
	 \end{choices}



\end{multicols}
\end{questions}

\end{document}
