% !TeX program = lualatex -synctex=1 -interaction=nonstopmode --shell-escape %.tex
\documentclass[international_finance_p1.tex]{subfiles}

\begin{document}

\section*{Literature}
\subsection*{Manuals}

\begin{frame}[shrink=15]
  \frametitle<presentation>{Manuals}
    
  \begin{thebibliography}{10}
    
  \beamertemplatebookbibitems
  % Start with overview books.

  \bibitem{Claessens2014}
	Claessens S., Kose M. A., Laeven L., Valencia F.
    \newblock {\em Financial Crises: Causes, Consequences, and Policy Responses.}.
    \newblock Washington D.C.: Intl Monetary Fund, 2014. 635 pages.
  \bibitem{Madura2012}
	Madura J.
	\newblock {\em International Financial Management.}
	\newblock USA: Cengage Learning, 2011. 736 pages. 
	
  \bibitem{Melvin2012}
	Melvin M.
	\newblock {\em International Money and Finance}
	\newblock Oxford, Academic Press, 2012. 336 pages.
  \bibitem{Hoboken2009}
	Shapiro A. C.
	\newblock {\em Multinational Financial Management}
	\newblock Hoboken, New Jersey: Wiley, 2009. 784 pages.
	\end{thebibliography}
\end{frame}
\subsection*{Legislature}
\begin{frame}{Legislature}
  \begin{thebibliography}{10}
    
  \beamertemplatearticlebibitems
  \bibitem{Curregul}
  	\newblock{\em
	Federal Law «On currency regulation and currency control» dated 10.12.2003 173-FZ (amended 12.03.2014 33-FZ) // SPS Konsul'tantPljus. URL: http://www.consultant.ru.}
	\end{thebibliography}
\end{frame}
\subsection*{Internet resources}
\begin{frame}[allowframebreaks]{Internet resources}
\begin{thebibliography}{10}
  \beamertemplatearticlebibitems
  \bibitem{Madura2012}
	MetaTrader 4. Trading Platform. 
	\newblock URL: http://www.metaquotes.net/ru.
  \bibitem{Madura2012}
	Vedomosti [Electronic resource]: newspaper. 
	\newblock URL: http://www.vedomosti.ru/.
  \bibitem{}
	Kommersant [Electronic resource]: newspaper.
	\newblock URL:http://www.kommersant.ru/daily/.
  \bibitem{}
	World Economy and International Relations [Electronic resource]: scientific journal.
	\newblock URL:http://www.imemo.ru.
  \bibitem{}
	Financial Times  [Electronic resource]: newspaper. 
	\newblock URL:http://www.ft.com/home/uk.
  \bibitem{}
	New York Times  [Electronic resource]: newspaper.
	\newblock URL:http://www.nytimes.com/.
  \bibitem{}
	Wall Street Journal [Electronic resource]: newspaper.
	\newblock URL:http://europe.wsj.com/home-page.
  \bibitem{}
	International Monetary Fund  [Electronic resource]: official site.
	\newblock URL:http://www.imf.org/external/russian/index.htm.
  \bibitem{}
	World Bank [Electronic resource]: official site.
	\newblock URL:http://web.worldbank.org.
  \bibitem{}
	World Trade Organization [Electronic resource]: official site.
	\newblock URL:http://www.wto.org/.
  \bibitem{}
	United Nations (UN) [Electronic resource]: official site.
	\newblock URL:http://www.unrussia.ru/public.html.
  \bibitem{}
	United Nations Industrial Development Organization (UNIDO) [Electronic resource]: official site. 
	\newblock URL:http://www.unido.org.
	\end{thebibliography}

\end{frame}

\subsection*{Lecture slides}
\begin{frame}
Lecture slides can be found at \url{www.academia.edu}:
\begin{thebibliography}{10}
	
	\setbeamertemplate{bibliography item}[online]
	
	\bibitem{acad}
	Academia
	
	\footnotesize{\url{https://unn-ru.academia.edu/AlexanderBorochkin}}
\end{thebibliography}
\end{frame}

\end{document}